\documentclass[letterpaper, 11pt, DIV = 10]{scrartcl}
\usepackage[]{lipsum}

\title{CSC 750-001 Group Formation and Problem Description}
\author{James Brown\and Ramesh Theerdhala\and Varshini Nallabothula\and Ram Vamshi Rudraram\and Chaitanya Latha Sevella}
\date{September 20, 2024}

\begin{document}
	\begin{titlepage}
		\maketitle
	\end{titlepage}
	
	\section*{Abstract and Goal}
		The midwestern United States is not nearly as well-supported with robust public transportation options as cities on both coasts do. In Springfield, you could argue that the best mode of public transit is Missouri State's BearLine. Furthermore, no passenger train service serves Springfield, MO at present. Therefore, we thought it would be appropriate to develop a project to better support the United States' current public transportation infrastructure, perhaps bringing to light the importance of having robust multimodal public transit throughout the country.
		
		Amtrak is the United States' main passenger train service, serving many areas nationwide. However, this service is not as well-known outside of the Northeast Corridor (NEC), where the service is used more frequently, and is better-supported. We think that publicizing the frequency of train service, where they're going, and their timetables in an interactive application would do a great deal in making Amtrak's service more accessible to the general public. % Add a more specific mention of the exact function of the app here?
		
	\section*{Planned Platform}
		We're planning on developing this project using JavaScript to create and customize the website, along with HTML/CSS to style the website as necessary.
		
	\section*{Objectives}
		\begin{itemize}
			\item To track status of Amtrak trains, providing data about the train's scheduled and actual departure and arrival times to and from each station
			\item To create a rich graphical user interface that makes the user experience as simple as possible to access the information provided by Amtrak's APIs
			\item To make a web application that can be compatible with several devices, regardless of the operating system and hardware being used 
		\end{itemize}
		
		
\end{document}